### 2019-09-12 tim-lucas-model-ensembles.tex
Add new results after fixing ml predictions at 0. Still weird though.

@@

\begin{table}
\caption{Machine learning model results and means of fitted parameters (i.e.\thinspace model weights) across cross-validation folds of the machine learning predictions only model. }
\centering
\small
\begin{tabular}{ll|rrrr}
     Country          & Model &      RMSE & $\beta_l $ &   $\beta_g$   &  $\beta_{g+l}$                                 \\ \hline
Madagascar & RF\textsubscript{l} & 0.100 & 0.337 &-&\\
Madagascar & RF\textsubscript{g} &  & - &&\\
Madagascar & GBM\textsubscript{l} & 0.109 & 0.450 & - &\\
Madagascar & GBM\textsubscript{g} &  & - &&\\
Madagascar & enet\textsubscript{l} & 0.100 & 0.326 &-&\\
Madagascar & enet\textsubscript{g} &  & - &&\\
Madagascar & nnet\textsubscript{l} & 0.113 & 0.031 &-&\\
Madagascar & nnet\textsubscript{g} &  & - &&\\
Madagascar & ppr\textsubscript{l} & 0.110 & -0.233 &-&\\
Madagascar & ppr\textsubscript{g} &  &  &&\vspace{0.3cm}\\ 
Colombia & RF\textsubscript{l} & 0.100 & 0.337 &-&\\
Colombia & RF\textsubscript{g} &  & - &&\\
Colombia & GBM\textsubscript{l} & 0.109 & 0.450 & - &\\
Colombia & GBM\textsubscript{g} &  & - &&\\
Colombia & enet\textsubscript{l} & 0.100 & 0.326 &-&\\
Colombia & enet\textsubscript{g} &  & - &&\\
Colombia & nnet\textsubscript{l} & 0.113 & 0.031 &-&\\
Colombia & nnet\textsubscript{g} &  & - &&\\
Colombia & ppr\textsubscript{l} & 0.110 & -0.233 &-&\\
Colombia & ppr\textsubscript{g} &  &  &&\vspace{0.3cm}\\ 
Senegal & RF\textsubscript{l} & 0.100 & 0.337 &-&\\
Senegal & RF\textsubscript{g} &  & - &&\\
Senegal & GBM\textsubscript{l} & 0.109 & 0.450 & - &\\
Senegal & GBM\textsubscript{g} &  & - &&\\
Senegal & enet\textsubscript{l} & 0.100 & 0.326 &-&\\
Senegal & enet\textsubscript{g} &  & - &&\\
Senegal & nnet\textsubscript{l} & 0.113 & 0.031 &-&\\
Senegal & nnet\textsubscript{g} &  & - &&\\
Senegal & ppr\textsubscript{l} & 0.110 & -0.233 &-&\\
Senegal & ppr\textsubscript{g} &  &  &&\vspace{0.3cm}\\ 
Indonesia & RF\textsubscript{l} & 0.100 & 0.337 &-&\\
Indonesia & RF\textsubscript{g} &  & - &&\\
Indonesia & GBM\textsubscript{l} & 0.109 & 0.450 & - &\\
Indonesia & GBM\textsubscript{g} &  & - &&\\
Indonesia & enet\textsubscript{l} & 0.100 & 0.326 &-&\\
Indonesia & enet\textsubscript{g} &  & - &&\\
Indonesia & nnet\textsubscript{l} & 0.113 & 0.031 &-&\\
Indonesia & nnet\textsubscript{g} &  & - &&\\
Indonesia & ppr\textsubscript{l} & 0.110 & -0.233 &-&\\
Indonesia & ppr\textsubscript{g} &  &  &&\\
\end{tabular}
\label{t:mlresults}
\end{table}

>>>>

\begin{table}[h!]
\caption{Pearson correlations between observed and predicted values. }
\centering
\begin{tabular}{llrrrr}
Cross-validation scheme & Country &  Covariates &  ML\textsubscript{l} &  ML\textsubscript{g} & ML\textsubscript{l} + ML\textsubscript{g} \\
\hline 
 Random &  Colombia & 0.58& 0.51 &   & 0.53 \\
 Random &  Madagascar &  0.70 &  \textbf{0.73} &   0.70 & 0.71 \\
 Random &  Senegal &  0.58 &  0.11 &  0.30 & 0.08 \\
 Random &  Indonesia &   &   &   &  \\
 Spatial &  Colombia &  0.12 &  0.09 &   & 0.10\\
 Spatial &  Madagascar &  0.22 &  \textbf{0.66} &  0.63 & 0.60\\
 Spatial &  Senegal &  0.63 &  0.27 &  0.36 & 0.35 \\
 Spatial &  Indonesia &   &   &   &  \\
\end{tabular}
\label{t:results}
\end{table}

@@

\begin{table}
\caption{Machine learning model results and means of fitted parameters (i.e.\thinspace model weights) across cross-validation folds of the machine learning predictions only model. }
\centering
\small
\begin{tabular}{ll|rrrr}
     Country          & Model &      RMSE & $\beta_l $ &   $\beta_g$   &  $\beta_{g+l}$                                 \\ \hline
Madagascar & RF\textsubscript{l} & 0.100 & 0.337 &-&\\
Madagascar & RF\textsubscript{g} &  0.169 & - &&\\
Madagascar & GBM\textsubscript{l} & 0.109 & 0.450 & - &\\
Madagascar & GBM\textsubscript{g} &  0.178& - &&\\
Madagascar & enet\textsubscript{l} & 0.100 & 0.326 &-&\\
Madagascar & enet\textsubscript{g} & 0.233 & - &&\\
Madagascar & nnet\textsubscript{l} & 0.113 & 0.031 &-&\\
Madagascar & nnet\textsubscript{g} &  0.220 & - &&\\
Madagascar & ppr\textsubscript{l} & 0.110 & -0.233 &-&\\
Madagascar & ppr\textsubscript{g} & 0.205 &  &&\vspace{0.3cm}\\ 
Colombia & RF\textsubscript{l} & 0.100 & 0.337 &-&\\
Colombia & RF\textsubscript{g} &  & - &&\\
Colombia & GBM\textsubscript{l} & 0.109 & 0.450 & - &\\
Colombia & GBM\textsubscript{g} &  & - &&\\
Colombia & enet\textsubscript{l} & 0.100 & 0.326 &-&\\
Colombia & enet\textsubscript{g} &  & - &&\\
Colombia & nnet\textsubscript{l} & 0.113 & 0.031 &-&\\
Colombia & nnet\textsubscript{g} &  & - &&\\
Colombia & ppr\textsubscript{l} & 0.110 & -0.233 &-&\\
Colombia & ppr\textsubscript{g} &  &  &&\vspace{0.3cm}\\ 
Senegal & RF\textsubscript{l} & 0.100 & 0.337 &-&\\
Senegal & RF\textsubscript{g} &  & - &&\\
Senegal & GBM\textsubscript{l} & 0.109 & 0.450 & - &\\
Senegal & GBM\textsubscript{g} &  & - &&\\
Senegal & enet\textsubscript{l} & 0.100 & 0.326 &-&\\
Senegal & enet\textsubscript{g} &  & - &&\\
Senegal & nnet\textsubscript{l} & 0.113 & 0.031 &-&\\
Senegal & nnet\textsubscript{g} &  & - &&\\
Senegal & ppr\textsubscript{l} & 0.110 & -0.233 &-&\\
Senegal & ppr\textsubscript{g} &  &  &&\vspace{0.3cm}\\ 
Indonesia & RF\textsubscript{l} & 0.100 & 0.337 &-&\\
Indonesia & RF\textsubscript{g} &  & - &&\\
Indonesia & GBM\textsubscript{l} & 0.109 & 0.450 & - &\\
Indonesia & GBM\textsubscript{g} &  & - &&\\
Indonesia & enet\textsubscript{l} & 0.100 & 0.326 &-&\\
Indonesia & enet\textsubscript{g} &  & - &&\\
Indonesia & nnet\textsubscript{l} & 0.113 & 0.031 &-&\\
Indonesia & nnet\textsubscript{g} &  & - &&\\
Indonesia & ppr\textsubscript{l} & 0.110 & -0.233 &-&\\
Indonesia & ppr\textsubscript{g} &  &  &&\\
\end{tabular}
\label{t:mlresults}
\end{table}
